\begin{document}
\section*{Military camp}

\subsection*{For All}
\begin{itemize}
        \item type of camp (which give approximatively the number of solider, La Guerre Romaine, Yann Le Bohec)
        \item time of activity of the camp and change of activity (idem)
        \item maybe more information about the amphorae using the CEIPAC DB (maybe approximate date, some productions site, but some data analysis to do before)
        \item theoretical consumption for each soldier (Remesal).
	\item informations found by jordi here : \url{http://dare.ht.lu.se/}
	\item private market? need to find references about that.
\item can we found cities close to the camp to see the impact of the evolution of the amphorae in the camp on the city.
\end{itemize}
\subsection*{Xanten}

Detailed review of all amphorae found there. Theoretically the CEIPAC database could help us to associates approximate dates and production sites with \emph{some} amphorae. We also have 'layer' where amphora were found,in the DB, can analyse it. Also more information here, but in German: \url{http://www.apx.lvr.de/de/roemische_stadt/roemische_stadt_1.html}

We could find other database like that (Mainz...)

\subsection*{Britannia}
        See Monfort : he speaks about proportion of type of amphora, productions site of those amphora for different periods (cf. JM presentation), and so about evolution of those proportion. We could also have more information using the CEIPAC database.

\section*{Pompei}
(Luce/Dani/Guillem)
Lot of data similar to Xanten but with more different types of amphora.
\begin{itemize}
        \item different markets
        \item archives problems
        \item infer amphora's date using greek name database
        \item interaction between market
        \item \ldots
\end{itemize}
\section*{Betica}
Olive Oil Production site. Information on production in : \emph{Economia oleica betica}, 1982
\begin{itemize}
        \item Sabada 1982 : production coast of olive oil base on Franck (cf below)
        \item Le cycle vegetatif de l'olivier: olive oil production (L/tree, fields size) given actual data on olive oil production
        \item Franck 1933-39 : Economic survey of Ancient Rome. How much it coast to produce olive oil
        \item Caton, Plinio (Naturae Historia) \& Columella for the primary sources.
\end{itemize}

\section*{Pecios}
"Theoritically" it could give idea on the commercial path. But only 70 sites, knowing that we found errors after looking 5 minutes to the datas\ldots
\end{document}

