\documentclass[12pt, b5paper,twoside]{tesi_upf}


%CODIFICATION
%\usepackage[latin1]{inputenc}
\usepackage{fontspec}


%LENGUAGE
\usepackage[english,catalan]{babel}

%ONLY TO OBTAIN MARK BANK INDEX INDICATION B5
\usepackage[b5paper]{geometry}
\usepackage[cam,a4,center,frame]{crop}

%INCLUDE GRAPHICS AND THE LOGO OF THE UPF
\usepackage{graphicx}

%FONTS TIMES OR GARAMOND, 
%\usepackage{New Roman}
\setmainfont{EB Garamond}

%WITHOUT HEADINGS: NO MODIFICATION
\pagestyle{plain}

%FOR THE INDEX OF SUBJECTS
\usepackage{makeidx}
\makeindex

%BIBLIOGRAPHY STYLE
\bibliographystyle{apalike}


%SELECT LANGUAGE
\selectlanguage{english}

%THE TABLE OF CONTENTS IS TITLE CONTENTS
\addto\captionscatalan
  {\renewcommand{\contentsname}{\Large \sffamily Sumari}}


%ADD YOUR DATA
\title{Social Change and Content Bias, a large scale analysis}
\subtitle{A model based approach of content-bias impact on large scale cultural change}
\author{Simon Carrignon}
\thyear{2019}
\department{}
\supervisor{Sergi Valverde \& Xavier Rubio-Campillo}


\begin{document}


\frontmatter

\maketitle

\cleardoublepage


%%%%%% Dedication

\noindent Pour ceux qui savent

\cleardoublepage

%%%%%% End dedication


%%%%%% Thanks
\noindent {\Large \sffamily Thanks} thanks to ceux qui savent et les autres

\cleardoublepage

%%%%%% End of thanks

%ABSTRACT IN TWO LEGUAGES.
\selectlanguage{english}
\section*{\Large \sffamily Abstract}
This is the abstract of the thesis in English.  Please, use less
than 150 words.

\selectlanguage{catalan}
\vspace*{\fill}
\section*{\Large \sffamily  Resum}
Vet aquí el resum de la tesi en català.  Si us plau, utilitzeu
menys de 150 paraules.
\vspace*{\fill}

\selectlanguage{english}
\cleardoublepage
%END OF ABSTRACT

%PREFACE. 
{\bf Preface}

\cleardoublepage
%END OF PREFACE


%TABLE OF CONTENTS: REQUIRED
\tableofcontents

%lIST OF FIGURES; ONLY IF THERE ARE FIGURES
\listoffigures
%TO APPER THE LIST OF FIGURES IN THE TABLE OF CONTENTS 
\addcontentsline{toc}{chapter}{List of figures}

%LIST OF TABLES; ONLY IF THERE ARE TABLES
\listoftables
%TO APPEAR THE LIST OF TABLES IN THE TABLE OF CONTENTS
\addcontentsline{toc}{chapter}{List of tables}

%START THE TEXT
\mainmatter


\chapter{ Introduction}

\section{Cultural Evolution (from darwin to Cultural Evolution theory)}
\subsection{ Evolutionary biology (Section 1 of Master tesis philosophy of science)}
\subsubsection{ History (darwin, mendel, modern synthesis, critics of modernr synthesis and adaptationist)}
\subsubsection{Methods and problems}
darwin need for artificial evolution and thought experiment, probel of `` how to prove NAtural selection'', problem of 
\subsection{How to study society and their evolution?}
\subsubsection{History}
\subsubsection{Cultural Evolution}
\subsubsection{Social Learning Strategies }
\subsection{Cultural Transmission \& Bias}
\subsubsection{ Social Learning Strategies}
\subsubsection{Critics toward transmission/imitation centered theories:}
Cognitivies attractors (Morin 2015) page 99 chapitre 3: The Myth of compulsive imitation
To solve that: intrinsic appeal
\subsubsection{ Need to study more complex strategies and more precisely (Kandler crtics on random mnidek)}
We face a problem: to study long term changes relying on complex cognitives transmission. How one can track on using the other? General simple models are good and quick but as mentionned by the critics need to be refined.
\section{ Model and Model Selection} (\emph{ie} how to study previous section)
\subsection{ Agent Base Modeling (Section 2 of master in philosophy of science \cite{carrignon2016modelandsimulaion}): }
With practical example from paper published between 2015 and 2018? \cite{montanier2016behavioralspecializationinembodiedevolutionaryroboticswhysodifficult},\cite{zibetti2015acaciaesanagentbasedmodelingandsimulationtoolforinvestigatingsocialbehaviorsinresourcelimitedtwodimensionalenvironments}\cite{medernach2016evolution})
\subsection{ Bayesian Inference (TRAJ paper section on baeysian inference)}
\chapter{ The limit of context dependant bias, a bayesian approach to online social media}
\section{ Simple context model (random neutral model, conformity and other frequency based bias)}
\section{ a case study with 10 years of online social media} (paper with Bentley and Ruck \cite{carrignon2018})
Some reflexion: chains of transmission \emph{are} wide. As imaginaned by Morin, p140
\chapter{'Meta Content': Economy and undirect access to content via success bias}
\section{Agent based model integrate Social Learning Stragies with economic changes, a theoretical exploration}
(Winter Simulation Conference paper \cite{carrignon2015modelingthecoevolutionoftradeandcultureinpastsocieties})
\section{ Historical case study ICRATES and ABC} (paper with Tom and Isa \cite{carrignon2018abmtrac})
\chapter{Conclusion}
       


\bibliography{../../biblio/bib/phd,../../biblio/bib/SimonCarrignon}



\backmatter
\printindex








\end{document}


%NUMBER OF THE EXTERNAL PAGE EXCEPT IN THE FIRST PAGE OF EACH CAPITAL
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot{}
\fancyfoot[RO]{\thepage}
\fancyfoot[LE]{\thepage}


%MULTIPLE INDEX
%In the preamble
\usepackage{multind}
\makeindex{authors}
%Introduction to form entries
\index{authors}{Einstein}
%Situation of the Index
\printindex{authors}{Author index}
%The \ usepakage {makeidx} \ makeindex \ printindex commands must be removed
%You need to exacute from the command line makeindex authors
