\documentclass[a4paper]{article}
\usepackage{fontspec}
\usepackage{geometry}

\geometry{margin=1in}

\title{EpNet Day lectures\\
Ortega et All : ABM of obsidian exchange.
}
\author{Simon Carrignon}
\date{2-11-2015}
\begin{document}
\maketitle

\section{General structure}
%Intro mat\& method \& result discussion \& Conclusion

They first introduce the archaeological/historical context : what is neolitic and and PPNA-B and then a short but strange explanation of difference between nomadims and sedentarism. With the ``central'' problem brought by sedentarisation : 
\begin{quote}
    dramatic results as fuluid intergroup interactions are crucial for sharing of information, resources and genes.
\end{quote}

Sedentarisation seems to be a challenge more than a solution.

Introduce the tool used : ABM and ethongraphic datas from new guinea

After that : raw ``result'' of the model in the 3/ Result following by a strange subpart 3.1 Discussion

Seems that the statistical data could be moved from discussion to result and a good separation between 3)Result and 4)Discussion could be made
\section{English}

\section{Clarity}

Some part of the model description remains unclear for me : 

\begin{itemize}
    \item what is distributed following poisson distribution?  (p.4 l. 25)
    \item How and why ``obsidian is introduced from the northern boundary?''  geological evidence ? (btw production equation is cut in the middle) (ibid)
\end{itemize}

I don't get neither the general idea of ``sedentarisation is a problem:network the solution''

\section{Links to similar works}


\section{Formulation of the model}

No algorithmic description of the model which would be good if at least the sources would be available somewhere. No clues neither about the technology used.

Where come from the two hypothesis on the new node attachment mechanisms?

Critics also made about our model : how variation arise ie how is defined the probability $p$ of creating new links? (p.5 l.1)
Important as this probability seem, looking to results, the more important factor

\section{Experiment design}

I found strange to use and display only the mean of the 100 runs for each parameters.
unquantified value of ``relevant parameter'' (we had the same problem with our model : what statistical test we used? )

\section{Results and interpretation}
They start by saying that the model demonstrate that ABM can be a powerful tool, I am not sure about the pertinence of this sentence given the way they built the article moreover this idea was not introduced before.

And again, it's seem that the paper is use to justify that 

Sendentarisation is the cause of the creation of complexe network, because sedentarisation \emph{need}
\begin{quote}
    sharing of information, resources and genes.
\end{quote}

Which seems strange or at least not very weel justified

\end{document}


