\documentclass[a4paper]{article}


%%%%lualatex on
%\usepackage{luatextra}
\usepackage{fontspec}
%Ligatures={Contextual, Common, Historical, Rare, Discretionary}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}

\usepackage{natbib}

\title{USS-SWC - 2015}
\author{Simon Carrignon}
\begin{document}
Simulation model, explantation and predection.

Experiment, theory, in between? what?

comes back to the matematic way to describe physical system.

Epistemic Opacity.


common myth : the more abstract, the less we understand.

idealization vs abstraction
idealization, like : friction=0 or an agent is rational

Final existance, but theoredinamical limit that need to be incompass by idealization in order to be understand.
so the assumptio of infinitu is absolutely necessar to understand the problem. 
(analyse of phase transition)



Has to be resolve
but is it an explanation?
opacity beause e need idealized oject to understand the objet, but what kinde of eplxantion we have?

In population genetics : frequency and fitness?

Varieant wiht time scale to larg eto bie observedd

Allele based model.


speaks about weldon, pearson, biostatistician : Weldon Pearson in which extend was not the problem of no Mendel?
o

How Fisher brings velocity distribution law in biology. Assuming an infinite number of factor responsible of a caracter

And central theorem (a infiinte number blabla follow a normally distribued law)


Mutation could be balanced by very small selection rates.


Afeter that : selection is statistical. 
but in biologie : a smooth limit vs a singular limit in biology.


\section{talk 2 : model vs experiment}
esy-1097993.loggreasy-1097993.log:q


\section{Talk Validation and Verification}
exploring the case of LHC. 

2 issues : 
accuracy (during the comparison)
adequacy of the comparison.


Make this kind of graph for history?


:)-< human behavior    | simulation
--> history


The validation could not be done!



\section{Validation, code validation}

Need a validation experiment
all unit, but it is impossible	
\end{document}

